
\cvsection{Education}
\cvevent{B.Tech. (CSE) - 7.4. SGPA}{JSS Academy of Technical Education}{ August 2018 -- Currently}{}
\cvevent{Diploma - 75\%}{Board Of Technical Education Uttar Pradesh}{July 2016 -- June 2018 }{}
\cvevent{HigherSecondary - 75\% }{Indian School Certificate}{ 2016 }{}
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Projects}
\cvproject{Hossip.com}
\begin{itemize}
\item Hossip is a portal which aim to close the gap between the recruiter and the talent. Designed and developed this website during my internship period..
\end{itemize}
\smallskip
\smallskip
\cvproject{Brainscore.fit}
\begin{itemize}
\item A series of games to boost your memory and to keep your brain running. Made during my internhsip period.
\end{itemize}
\smallskip
\smallskip
\cvproject{Wild Weather}
\begin{itemize}
\item A very minimalist weather app that gives you a detailed overview of the weather. Supports multiple languages and units. Build using React native and expo.
\end{itemize}
\smallskip
\smallskip
\cvproject{Todoist}
\begin{itemize}
\item A modern take at classical to-do app. Built using React with main focus being the design of the app.
\end{itemize}
\smallskip
\smallskip
\cvproject{Saletancy}
\begin{itemize}
\item A B2B ecommerce website made during my first internship. A complete solution for all your ecommerce needs.
\end{itemize}
\smallskip
\smallskip
\cvproject{InStories}
\begin{itemize}
\item An Instagram stories maker made during the Innovaccer hackathon. Tech used are React, Python and few AI libraries.
\end{itemize}
\cvproject{}